A simple visual alternative to all pairwise comparisons

### 2024-06-25 text/22/analysis-of-means.Rmd

where $\bar Y_{..}$ is the overall mean and $h(\alpha, t, N)$ comes from a table such as [this one][lev1] (see page 3) or [this one][sim3].

@@

[sim3]: http://www.pmean.com/07/AnomTable05Part1.html

>>>>

where $\bar Y_{..}$ is the overall mean and $h(\alpha, t, N)$ comes from a table such as [this one][lev1] (see page 3) or [this one][sim3a].

@@

[sim3a]: http://www.pmean.com/07/AnomTable05Part1.html
